Disagreement Regarding 2016 Presidential Election in the United States^[Code and data are available at: https://github.com/SANGWOONG-LEE/Thailand_Healthcare]

### 2022-04-02 outputs/paper/paper.Rmd
ggplot

# Data
```{r, include=FALSE, echo=FALSE}
# Read the extracted and cleaned data, data extraction done in 01-gather-data.R and modification done in 02-clean-and-prepare-data.R
data <- read_csv("outputs/data/cleaned_data.csv")
```

```{r}
data %>%
  ggplot(aes(x = Variable, y = Health_Record)) +
  geom_bar(stat='identity') +
  coord_flip()
```

Talk more about it.

>>>>

# Data
```{r, include=FALSE, echo=FALSE}
# Read the extracted and cleaned data, data extraction done in 01-gather-data.R and modification done in 02-clean-and-prepare-data.R
data <- read_csv("outputs/data/cleaned_data.csv")

# create new dataset only for urban-rural data
urban_rural <- data.frame(location = c(rep("urban", data[1,6]), rep("rural", data[2,6])),
                immune_data =  c(rep("Health Report", round(data[1,2]*data[1,6]/100)), rep("Mothers Report", round(data[1,3]*data[1,6]/100)), rep("No immune", round(data[1,5]*data[1,6]/100)), 
                                 rep("Health Report", round(data[2,2]*data[2,6]/100)), rep("Mothers Report", round(data[2,3]*data[2,6]/100)), rep("No immune", round(data[2,5]*data[2,6]/100)))

                )

# create new dataset only for for region
region <- data.frame(region = c(rep("north", data[3,6]), rep("north_east", data[4,6]), rep("central", data[5,6]), rep("south", data[6,6]), rep("bangkok", data[7,6])),
                    immune_data =  c(rep("Health Report", round(data[3,2]*data[3,6]/100)), rep("Mothers Report", round(data[3,3]*data[3,6]/100)), rep("No immune", round(data[3,5]*data[3,6]/100)), 
                                 rep("Health Report", round(data[4,2]*data[4,6]/100)), rep("Mothers Report", round(data[4,3]*data[4,6]/100)), rep("No immune", round(data[4,5]*data[4,6]/100)),
                                 rep("Health Report", round(data[5,2]*data[5,6]/100)), rep("Mothers Report", round(data[5,3]*data[5,6]/100)), rep("No immune", round(data[5,5]*data[5,6]/100)), 
                                 rep("Health Report", round(data[6,2]*data[6,6]/100)), rep("Mothers Report", round(data[6,3]*data[6,6]/100)), rep("No immune", round(data[6,5]*data[6,6]/100)),
                                 rep("Health Report", round(data[7,2]*data[7,6]/100)), rep("Mothers Report", round(data[7,3]*data[7,6]/100)), rep("No immune", round(data[7,5]*data[7,6]/100)))
                    )

# create new dataset only for for education

 # no_edu <-data.frame(education = c(rep("no_edu", 265)),
 #                     immune_data = c(rep("Health Report", round(data[8,2]*data[8,6]/100)), rep("Mothers Report", round(data[8,3]*data[8,6]/100)), rep("No immune", round(data[8,5]*data[8,6]/100)))
 #                     )
 # 
 # primary <-data.frame(education = c(rep("primary", data[9,6])),
 #                     immune_data = c(rep("Health Report", round(data[9,2]*data[9,6]/100)), rep("Mothers Report", floor(data[9,3]*data[9,6]/100)), rep("No immune", round(data[9,5]*data[9,6]/100)))
 #                     )
 # 
 # secondary <-data.frame(education = c(rep("secondary", data[10,6])),
 #                     immune_data = c(rep("Health Report", floor(data[10,2]*data[10,6]/100)), rep("Mothers Report", floor(data[10,3]*data[10,6]/100)), rep("No immune", round(data[10,5]*data[10,6]/100)))
 #                    )
# education <- data.frame(education = c(rep("no_education", data[8,6]), rep("primary", data[9,6]), rep("secondary", data[10,6]), rep("higher", data[11,6])),
#                     immune_data =  c(rep("Health Report", round(data[8,2]*data[8,6]/100)), rep("Mothers Report", round(data[8,3]*data[8,6]/100)), rep("No immune", round(data[8,5]*data[8,6]/100)), 
#                                  rep("Health Report", round(data[9,2]*data[9,6]/100)), rep("Mothers Report", round(data[9,3]*data[9,6]/100)), rep("No immune", round(data[9,5]*data[9,6]/100)),
#                                  rep("Health Report", round(data[10,2]*data[10,6]/100)), rep("Mothers Report", round(data[10,3]*data[10,6]/100)), rep("No immune", round(data[10,5]*data[10,6]/100)), 
#                                  rep("Health Report", round(data[11,2]*data[11,6]/100)), rep("Mothers Report", round(data[11,3]*data[11,6]/100)), rep("No immune", round(data[11,5]*data[11,6]/100)))
#                     )

# create new dataset only for for education
religion <- data.frame(religion = c(rep("Buddhist", data[12,6]), rep("Islam", data[13,6])),
                immune_data =  c(rep("Health Report", round(data[12,2]*data[12,6]/100)), rep("Mothers Report", round(data[12,3]*data[12,6]/100)), rep("No immune", round(data[12,5]*data[12,6]/100)), 
                                 rep("Health Report", round(data[13,2]*data[13,6]/100)), rep("Mothers Report", round(data[13,3]*data[13,6]/100)), rep("No immune", round(data[13,5]*data[13,6]/100)))
                      )
```

```{r}
#ggplot(data[1:2,], aes(x = Variable, y = Health_Record)) + geom_bar(stat='identity') + facet_wrap(~Mothers_Report)
urban_rural %>%
  ggplot(aes(x = location, fill = immune_data)) +
  geom_bar(position = "dodge")
```
```{r}
#ggplot(data[3:7,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
region %>%
  ggplot(aes(x = region, fill = immune_data)) +
  geom_bar(position = "dodge")
```
```{r}
#ggplot(data[8:11,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
```
```{r}
#ggplot(data[12:13,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
religion %>%
  ggplot(aes(x = religion, fill = immune_data)) +
  geom_bar(position = "dodge")
```
Talk more about it.
